Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
fixed mentioned typos

GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}. Prost however midly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.

>>>>

GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}. Prost however mildly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
